---
title: "Title"
subtitle: "Supplementary Materials"

author:
- William M. Oldham:
    institute: bwh
    correspondence: true
    email: woldham@bwh.harvard.edu
    
institute:
- bwh: Department of Medicine, Brigham and Women's Hospital and Harvard Medical School, Boston, MA

bibliography_main: library.json
bibliography_software: packages.bib
csl: cell-metabolism.csl
link-citations: yes

output:
  bookdown::word_document2:
    reference_docx: !expr system.file("manuscript", "template.docx", package = "McGarrity.2022.hypoxia.omics")
    df_print: kable
    number_sections: false
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
      - '--lua-filter=pagebreak.lua'
      - '--lua-filter=multiple-bibliographies.lua'

compact-title: true
geometry: margin = 0.75in
fontsize: 11pt
mainfont: Calibri
graphics: yes

nocite: |
  @R-base, @R-bookdown, @R-devtools, @R-dplyr, @R-emmeans, @R-forcats, @R-ggplot2, 
  @R-kableExtra, @R-knitr, @R-lme4, @R-lmerTest, @R-lubridate, @R-magick, @R-magrittr, 
  @R-MASS, @R-patchwork, @R-pbkrtest, @R-purrr, @R-RColorBrewer, @R-readr, 
  @R-readxl, @R-renv, @R-rlang, @R-rmarkdown, @R-roxygen2, @R-stringr, @R-tibble, 
  @R-tidyr, @R-tidyverse, @R-tinytex, @R-usethis, @R-viridis, @R-wmo, 
  @bookdown2016, @ggplot22016, @knitr2015, @lme42015, @lmerTest2017, @lubridate2011, 
  @MASS2002, @pbkrtest2014, @rmarkdown2018, @tidyverse2019, tinytex2019
---

```{r setup, include = FALSE}
# library(X)
devtools::load_all()

knitr::opts_chunk$set(
  echo = FALSE, 
  warning = FALSE, 
  message = FALSE, 
  out.width = "80%", 
  out.extra = ""
)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

knitr::opts_knit$set(kable.force.latex = FALSE)

options(tinytex.verbose = TRUE)

targets::tar_load(
  c(
    s1_figure, 
  )
)
```

\newpage 

# References

::: {#refs_main} 
:::

## Software

::: {#refs_software} 
:::

\newpage

# Tables

\newpage

# Figure legends

(ref:s1) **Metabolomic profiling of hypoxic lung fibroblasts.** Lung fibroblasts (LFs) were exposed to 0.2% oxygen for 24 h prior to metabolite extraction and targeted LC-MS metabolomic profiling. (**A**) Volcano plot of polar intracellular metabolites. (**B**) Volcano plot of polar extracellular metabolites. (**C**) Volcano plot of lipid intracellular metabolites. Differential expression was determined from five biological replicates by linear modeling. Probability values were adjusted using a false discovery rate < 0.05. The top 10 increased and decreased metabolites are labeled. Metabolite classes are color-coded based on biochemical pathway (PPP, pentose phosphate pathway; TCA, tricarboxylic acid cycle). (**B**) Venn diagram demonstrating the overlap among significantly differentially regulated intracellular metabolites in LFs compared to PAECs and PASMCs. Fewer metabolites were included in the metabolomic profiling of LFs.

```{r}
figs <- 
  list.files(
    system.file(
      "manuscript/figures", 
      package = "McGarrity.2022.hypoxia.omics"
    ), 
    pattern = "s\\d{1}\\.png"
  ) %>% 
  rlang::set_names(stringr::str_extract(., "^.*(?=\\.png)"))
```

```{r results = "asis"}
out <- 
  purrr::imap(
    figs, 
    ~ cat("Supplementary Figure ", stringr::str_extract(.y, "\\d"), ": (ref:", .y, ")\n\n", sep = "")
  )
```

\newpage

# Figures

```{r s1, fig.cap = "(ref:s1)"}
knitr::include_graphics(
  system.file(
    "manuscript/figures/s1.png",
    package = "McGarrity.2022.hypoxia.omics"
  )
)
```
